\newpage

\section{Related Work}
\label{sec:related-work}

\para{Model Serving.} Frameworks such as Clipper~\cite{crankshaw2017clipper} and
TensorFlow Serving~\cite{tensorflow2017serving} only focus on system-level
techniques such as batching and hardware acceleration to improve
throughput. While Clipper allows ensemble of models, the purpose is to improve
accuracy at the cost of resources. Both frameworks have poor performance when
under overload.

\para{Mobile-Cloud Offloading.} Prior offloading framework, such as
MAUI~\cite{cuervo2010maui}, CloneCloud~\cite{chun2011clonecloud},
Gabriel~\cite{ha2014towards}, and Tango~\cite{gordon2015accelerating}, runs the
same algorithm (with the same configurations) across different machines: a poor
match for the future heterogeneous mobile-edge-cloud (MEC)
environment. \sysname{} explicitly models performance and select the appropriate
algorithm and configuration at runtime.

\para{Low Latency via Redundancy.} The idea of initiating redundant operations
across diverse resources and using the first result which completes has been
explored in many contexts, such as cloud
computing~\cite{ananthanarayanan2013effective}, cloud
service~\cite{dean2013tail}, wide-area network service~\cite{vulimiri2013low},
and mobile applications~\cite{gordon2015accelerating}. We extends the redundancy
and offer a variety of policies for combining results from multiple services.

\para{Approximate Techniques.} With the increasing workload to handle, recent
systems~\cite{agarwal2013blinkdb, rabkin2014aggregation, zhang2017live}
recognizes that timely-despite-inaccurate results are better than late
results.

\para{Bayesian Optimization.} To optimize complex systems in a principled way,
many frameworks employ Bayesian Optimizations to tune application behavior, such
as CherryPick~\cite{alipourfard2017cherrypick}, FLASH~\cite{zhang2016flash}, and
BOAT~\cite{dalibard2017boat}. These frameworks focus on single-objective
optimization: minimizing job completion time or maximizing application
accuracy. In contrast, \sysname{} addresses a multi-dimensional optimization
between application accuracy and processing times. We demonstrated that BO
outperforms greedy heuristic approach used in VideoStorm~\cite{zhang2017live}.

\para{SLO-awareness.} MittOS~\cite{hao2017mittos} advocates the return of
\texttt{EBUSY} for IO operations to bound IO requests.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../serving"
%%% End:
