\documentclass[thesis.tex]{subfiles}

\begin{document}

\begin{acknowledgements}

  First and foremost, I would like to thank my advisor Prof.\,Edward Lee for his
  guidance and support in the past six years. Like most Ph.D. journeys, there
  were multiple occasions that I felt desperately frustrated, especially when I
  was stuck in a problem or could not see the value of my work. At those times,
  all I need was to have a meeting with Edward. He has a kind of magic that
  sweeps frustration away. With his breath of knowledge and ability to connect
  insights from diverse topics, I always left his office feeling inspired and
  encouraged. I have learned so much from Edward, including building
  proof-of-concepts (he still writes a lot of code), giving credit to people,
  valuing collaboration, and communicating ideas effectively. It is my great
  privilege to be his Ph.D. student.

  During my Ph.D., I am mostly involved with the TerraSwarm project, which
  allowed me to collaborate with many outstanding researchers and
  professors. Prof.\,Bj\"orn Hartmann mentored me in my first project, from
  which I learned many practical research skills: how to brainstorm novel ideas,
  set a research agenda, write a paper, design graphics,\footnote{The figure
    showing an augmented version of Google Glass is used on the web page of
    \href{https://eecs.berkeley.edu/research}{Research at Berkeley EECS}.}
  revise a paper, and give a conference talk. Later, with Prof.\,John
  Kubiatowicz and many other folks in the Global Data Plane project, we wrote a
  position paper with a fun title: ``The Cloud is Not Enough.'' Dr.\,David
  Mellis agreed to collaborate with me after we met in a TerraSwarm poster
  session. Our collaboration introduced me to many software engineer practices
  and I became a heavy user of GitHub afterwards. Prof.\,John Wawrzynek offered
  invaluable feedback in the last few years of my Ph.D. Our discussion began
  with a grand SwarmOS vision and evolved into a specific direction on
  adaptation, i.e., this thesis.

  I would like to thank Prof.\,Syliva Ratnasamy and Prof.\,John Chuang for being
  on my thesis committee and offering their feedback. Sylvia taught me to ask
  fundamental questions about the swarm and how it would change the status
  quo. John, with his experience in many novel applications, offered
  perspectives from a broader context.

  I especially thank Prof.\,Xin Jin and feel grateful to have the chance to
  collaborate with him. I met him when he was a postdoc at Berkeley and was
  impressed by his knowledge and ideas in system research. Xin pointed me to
  JetStream and our discussion led to exploring systematic adaptation. He is
  also a master for system evaluation, a skill often considered as black art. He
  taught me how to design evaluation goals, run experiments, and present the
  results in compelling figures.

  I am thankful for my undergraduate research experience that builds the
  foundation for my research in the swarm. I must thank my MSRA mentor
  Prof.\,Xiaofan Fred Jiang, without whom I may not have pursued a Ph.D. or come
  to Berkeley. In my undergraduate study, I have also received much help and
  guidance from Prof.\,Lin Zhang.

  I really enjoy my stay in the DOP center. The friendly atmosphere and the
  inspiring conversations with colleagues/friends have helped me march on in the
  grinding Ph.D. experience. I am lucky to have shared 545K with Eunsuk Kang,
  Ilge Akkaya, Eleftherios Matsikoudis and 545N with Mehrdad Niknami. We would
  chat about anything when it comes to a research break. I came to Berkeley
  around the same time with Hokeun Kim, Marten Lohstroh, Antonio Iannopollo, and
  Ankush Desai. I feel sincerely grateful to have the chance to grow together
  with you towards independent researchers. I also feel fortunate to have met
  and learned from other past and current members of the Ptolemy
  group---Patricia Derler, Chris Shaver (Yvan Vivid), Michael Zimmer, Christos
  Stergiou, Dai Bui, Ben Lickly, Matt Weber, and Gil Lederman.

  When it comes to logistics, Mary Stewart and Christopher Brooks are
  undoubtedly the best. Mary deals with the physical side and Christopher
  manages the cyber side. I am extremely impressed by and would like to learn
  Christopher's management skills, be it project, software, or life. His email
  ``New Year's Cleanup'' in 2013 was an eye-opener to me about tidying up
  digital assets. Thank you for keeping my graduate life easy off the boring
  office chores and logistics.

  A great part of Edward's research group is that there are always visiting
  scholars. Over the past few years, I have met researchers with
  shockingly-broad backgrounds---Shuhei Emoto, Marjan Sirjani, Joseph Ng,
  Chadlia Jerad Ep Ben Haj Hmida, Moez Ben Haj Hmida, Maryam Bagheri, Victor
  Nouvellet, Atul Sandur, Andr\'es Goen, Ravi Akella, and many others.

  I would also like to thank other students, researchers and collaborators I
  have worked with closely---Yu-Hsiang Sean Chen, Claire Tuna, Achal Dave for
  the Google Glass project, Ahir Reddy for a wide-area network measurement
  project, and Nitesh Mor, Jack Kolb, Eric Allman for the Global Data Plane.

  Graduate life would have become monotonous without friends to take my mind off
  the stress. Thank you---Kaifei Chen, Qifan Pu, Xiang Gao, Peihan Miao, Yuting
  Wei, Chaoran Guo, Yiyan Ge, Tianshi Wang, Zhuo Chen, Dezhi Hong---for many
  memorable moments.

  Berkeley and nearby cities, Emeryville, Oakland, Albany, El Cerrito, are by
  far the best place I have lived. Despite living on a budget as a poor graduate
  student, I still felt great happiness, because of many local stores: Monterey
  Market, Berkeley Bowl, Cheese Board, Acme Bread, Blue Bottle Coffee, Sweet
  Maria's, Yaoya-san, the Local Butcher Shop and more that I refrained from
  listing due to space constrains.

  Last but not least, I am grateful to my family: my parents and my
  sister. While my physical distance is moving further away from home---Zhouzhi
  in the same town, Xi'an in the same city, Beijing in the same country, now
  Berkeley, on the same planet---you have always been there with your unwavering
  support and unconditional love. I would especially like to thank my girlfriend
  Limin Chen. Our love has endured the test of time, time zone difference, and
  long distance. Thank you for your love, company, encouragement, and
  sacrifices.

\end{acknowledgements}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
