\documentclass[thesis.tex]{subfiles}

\begin{document}

\chapter{Background and Motivation}
\label{cha:background}

In this chapter, we first show the trends of swarm applications and how they
differ from previous topics, such as wireless sensor networks, cyber-physical
systems and ubiquitous computing. By analyzing the fundamental properties of
swarm applications, we summarize the core challenges with developing swarm
applications, such as constrained resources and heterogeneous environment.

One key potential with swarm applications is due to the scale facilitated by the
inter-connectivity, especially as the cloud becomes mature and is used as the
universal computation and storage backend. Many applications are constructed by
directly connecting devices to the cloud. This trend, although understandable,
is not the best long term approach. We discuss the pitfalls with this
cloud-centric approach and argue that ``the cloud is not enough.''

To accompany the cloud, a new tier of computing infrastructure, the edge,
arises. Due to its close proximity to end devices, the edge is effective to
reduce network latency and provide more resource guarantees to end
devices. However, unlike the cloud, the edge is resource constrained and it is
unclear what capabilities we can expect from the edge. As a result, swarm
applications relying on the edge need to take the heterogeneous landscape into
account.

\input{background/swarm}
\input{background/cloud}
\input{background/cloud-pitfalls}
\input{background/edge}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
