\chapter{Thesis Plan}
\label{cha:thesis-plan}

This thesis aims to make the following statement: a system-level design that
empowers adaptation in an automatic way will enable the resilient execution of
diverse streaming applications.

The current research results presented in this manuscript, i.e.\,the proposal,
demonstrate how such a design achieves a balance between delay and application
utility in the presence of network resource variation.

The complete thesis will extend the current work to a more holistic framework.
Specifically, I plan to work on the following two directions (see
\autoref{tab:plan} for the concrete timeline):

\para{Multitask resource allocation:} Many streaming applications will co-exist
and share the infrastructure. When uncoordinated, they will compete for
resources such as the network bandwidth. While the adaptation strategy may be
optimal for each application, taking them collectively, the system may not be at
an optimal state. In this direction, I will study the multitask resource
allocation and how it can adapt each streaming applications for an overall
maximal utility.

\para{Adaptation to computing resources:} In addition to network resources, the
computing resources also have a large variation across the heterogeneous
platforms. The available platforms range from embedded devices to powerful
rack-level machines. Also, the availability of the platforms is not always
guaranteed: nodes join and leave; the connectivity may be completely cut off. In
this direction, I will study how to adapt applications to different
configurations of the computing resources.

\vspace{1.5em}
\begin{table}[h]
  \normalsize
  \centering
  \begin{tabular}{r l}
    \toprule
    \textbf{Time} & \textbf{Research Topic} \\
    \midrule
    Spring 2017 & Resource allocation among multiple streaming applications \\
    Summer 2017 & Preliminary study on adaptation to computing resources \\
    Fall 2017 & Combine network and compute resources for a holistic control plane \\
    Spring 2018 &  Finish the thesis \\
    \bottomrule
  \end{tabular}
  \caption{Thesis Timeline}
  \label{tab:plan}
\end{table}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:
