\documentclass[thesis.tex]{subfiles}

\begin{document}

\chapter{Network Resource Adaptation}
\label{cha:netw-reso-adapt}

In this chapter, we focus on swarm applications adapting to network
resources. Specifically, we target at swarm applications that rely on wide-area
streaming and perform analytics elsewhere, e.g., the cloud. These streaming
applications face the challenge of scarce and variable wide-area network (WAN)
bandwidth. Many applications today are built directly with TCP or UDP, and they
suffer from increased latency or degraded accuracy. State-of-the-art approaches
that adapt to network changes require developer writing sub-optimal manual
policies or are limited to application-specific optimizations.

We present \awstream{}, a stream processing system that uses adaptation to
simultaneously achieve low latency and high accuracy in the wide area, requiring
minimal developer efforts. To realize this, \awstream{} follows our proposed
methodology: $(i)$ it integrates application adaptation as a first-class
programming abstraction in the stream processing model; $(ii)$ with a
combination of offline and online profiling, it automatically learns an accurate
profile that models accuracy and bandwidth trade-off; and $(iii)$ at runtime, it
carefully adjusts the application data rate to match the available bandwidth
while maximizing the achievable accuracy. We evaluate \awstream{} with three
real-world applications: augmented reality, pedestrian detection, and monitoring
log analysis. Our experiments show that \awstream{} achieves sub-second latency
with only nominal accuracy drop (2-6\%).

\input{awstream/intro}
\input{awstream/motivation}
\input{awstream/system}
\input{awstream/impl}
\input{awstream/evaluation}
\input{awstream/hls}
\input{awstream/jetstream}
\input{awstream/discussion}
\input{awstream/conclusion}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
