\section{Chapter Summary}
\label{sec:chap-summary}

Swarm applications that rely on computation-heavy tasks face the challenge of
heterogeneous compute capabilities and variable network/service load. Without
adaptation, the computation tasks would miss the deadline, which hurts user
experience. In order to provide bounded response times, we propose to adapt
computation based on a performance model that characterizes the trade-off
between application accuracy and processing times.

Performance modeling for computation adaptation is challenging due to the large
parameter space and heterogeneous device capabilities. This chapter focuses on
improving the profiling efficiency with two techniques:

\begin{itemize}[topsep=5pt, itemsep=5pt]
\item We use Bayesian Optimization (BO) to address the large parameter space. BO
  models black-box function and iteratively proposes new sample points that are
  more likely to be in the Pareto-optimal set. Using Viola-Jones face detector
  as a case study, we demonstrate that BO reduces the number of samples needed
  by more than 50$\times$, compared to exhaustive search. Compared with other
  proposed approaches (random search and coordinate search), BO finds better
  Pareto-optimal configurations with the same search budget.
\item We use profile transfer to address heterogeneous device capabilities. New
  devices update an existing profile by only measuring the processing times of
  Pareto-optimal configurations. The profile transfer eliminates the need to get
  all training data, evaluate the algorithm for all data, and run BO engine. We
  have empirically validated profile transfer with VJ face detector.
\end{itemize}

The profile can guide an application to select an operating point that meets a
response deadline. An advanced use of the profile is to guide a model serving
system to make scheduling decisions. For example, the server can degrade the
accuracy for a subset of requests to improve its overall throughput. In this
thesis, we have focused on profiling, and the use of the profile at runtime is
left as a future work.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../compute"
%%% End:
